---
title: "Data 550 Midterm Project Report"
author: "Tracy Huang, Guadalupe Rivera, Yingte Liu, Jiali Guo"
date: "`r Sys.Date()`"
output: html_document
params: 
  text: display
---

This report contains some descriptive analyses of the f75 dataset, which contains data from a randomized trial testing whether a modified milk formula (f75) improves outcomes for children with severe acute malnutrition (first 6-months of data from year-long study).

```{r, set-chunk-opts, echo = FALSE}
library(knitr)
library(here)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
here::i_am("report.Rmd")

# read in data 
path = here()
data = read.csv(paste(path,"/Raw_Data/f75_interim.csv",sep=""))
```

# Descriptive Analysis

## Tabular analysis

A descriptive table is below.

```{r, table1}
table <- readRDS(
  file = here::here("Output/table_one.rds")
)
table
```

## Graphical analysis

Below we report a mosaic plot. 

```{r, mosaic plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("Output/mosaicplot.png")
)
```

Below we report two boxplots.

```{r, boxplot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("Output/box_plot1.png")
)

#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("Output/box_plot2.png")
)
```
